---
title: "DoubletFinder to remove doublets in perturb-seq data"
author: "Zhiyuan Hu"
date: '2023-09-02 (last modified: `r Sys.Date()`)'
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(Seurat)
# library(patchwork)
library(RColorBrewer)
library(scales)
library(DoubletFinder)
stage_cols <- RColorBrewer::brewer.pal("Spectral", n = 11)
genotype_cols <- RColorBrewer::brewer.pal("Set2", n = 8)[c(1,2,3,8)]
sample_cols <- RColorBrewer::brewer.pal("Accent", n = 8)
doublet_cols <- RColorBrewer::brewer.pal("Paired", n = 8)[c(6,8,2)]
```

# Read data

```{r}
seu <- readRDS("perturb_seq/analysis/clustering/output_p1top11/seu_all_clustered.rds")
table(seu$sample)
```

# Doublet filter

Refer to this https://www.epfl.ch/research/facilities/gene-expression-core-facility/wp-content/uploads/2021/04/Multiome-10XG-samples-preparation-guidelines-by-GECF-vA.01.pdf

```{r}
doublet_rates <- c(0.02, 0.016, 0.039,0.008,0.012,0.014,0.032,0.02,0.02)
names(doublet_rates) <- c("p1","p2","p3","p5","p6","p8","p9","p10","p11")
```

## p1

```{r}
sample_itor <- "p1"
seu_1 <- seu[,seu$sample == sample_itor]

## Pre-process Seurat object (standard) --------------------------------------------------------------------------------------
seu_1 <- NormalizeData(seu_1)
seu_1 <- FindVariableFeatures(seu_1, selection.method = "vst", nfeatures = 2000)
seu_1 <- ScaleData(seu_1)
seu_1 <- RunPCA(seu_1)
seu_1 <- RunTSNE(seu_1, dims = 1:20)
seu_1 <- FindNeighbors(object = seu_1, reduction = "pca", dims = 1:20, verbose = TRUE)
seu_1 <- FindClusters(seu_1, dims = 1:20, resolution = 0.6)
## pK Identification (no ground-truth) ---------------------------------------------------------------------------------------
sweep.res.list <- paramSweep_v3(seu_1, PCs = 1:20, sct = FALSE)
sweep.stats <- summarizeSweep(sweep.res.list, GT = FALSE)
bcmvn <- find.pK(sweep.stats)
bcmvn

## Homotypic Doublet Proportion Estimate -------------------------------------------------------------------------------------
annotations <- seu_1@meta.data$seurat_clusters
homotypic.prop <- modelHomotypic(annotations)           ## ex: annotations <- seu@meta.data$ClusteringResults
nExp_poi <- round(doublet_rates[sample_itor]*nrow(seu_1@meta.data))  ## Assuming 7.5% doublet formation rate - tailor for your dataset
nExp_poi.adj <- round(nExp_poi*(1-homotypic.prop))

## Run DoubletFinder with varying classification stringencies ----------------------------------------------------------------
seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.005, nExp = nExp_poi, reuse.pANN = FALSE, sct = FALSE)
seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.005, nExp = nExp_poi.adj, reuse.pANN = FALSE, sct = FALSE)

seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.02, nExp = nExp_poi, reuse.pANN = FALSE, sct = FALSE)
seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.02, nExp = nExp_poi.adj, reuse.pANN = FALSE, sct = FALSE)

## Assign classification
seu_1$DoubletFinder <- "Singlet"
seu_1$DoubletFinder[seu_1$DF.classifications_0.25_0.005_66 == "Doublet"] <- "Doublet (high likelyhood)"
seu_1$DoubletFinder[seu_1$DF.classifications_0.25_0.005_66 != "Doublet" &
                    seu_1$DF.classifications_0.25_0.005_71 == "Doublet"] <- "Doublet (low likelyhood)"

## Assign classification
seu_1$DoubletFinder_pK <- "Singlet"
seu_1$DoubletFinder_pK[seu_1$DF.classifications_0.25_0.02_66 == "Doublet"] <- "Doublet (high likelyhood)"
seu_1$DoubletFinder_pK[seu_1$DF.classifications_0.25_0.02_66 != "Doublet" &
                          seu_1$DF.classifications_0.25_0.02_71 == "Doublet"] <- "Doublet (low likelyhood)"
```

We are viewing two pK values due to this potential issue https://github.com/chris-mcginnis-ucsf/DoubletFinder/issues/130

```{r, fig.width=12, fig.height=4}
p1 <- DimPlot(seu_1, group.by = "DoubletFinder")
p2 <- DimPlot(seu_1, group.by = "DoubletFinder_pK")
p1 + p2
```

```{r, fig.width=12, fig.height=4}
p1 <- VlnPlot(seu_1, features = c("nFeature_RNA"), group.by = "DoubletFinder" , pt.size =  0.01)
p2 <- VlnPlot(seu_1, features = c("nFeature_RNA"), group.by = "DoubletFinder_pK", pt.size =  0.01)
cowplot::plot_grid(p1, p2, ncol = 2)
```

```{r}
seu$DoubletFinder <- NA
seu$DoubletFinder[match(colnames(seu_1), colnames(seu))] <- seu_1$DoubletFinder
```


## p2


```{r}
sample_itor <- "p2"
seu_1 <- seu[,seu$sample == sample_itor]

## Pre-process Seurat object (standard) --------------------------------------------------------------------------------------
seu_1 <- NormalizeData(seu_1)
seu_1 <- FindVariableFeatures(seu_1, selection.method = "vst", nfeatures = 2000)
seu_1 <- ScaleData(seu_1)
seu_1 <- RunPCA(seu_1)
seu_1 <- RunTSNE(seu_1, dims = 1:20)
seu_1 <- FindNeighbors(object = seu_1, reduction = "pca", dims = 1:20, verbose = TRUE)
seu_1 <- FindClusters(seu_1, dims = 1:20, resolution = 0.6)
## pK Identification (no ground-truth) ---------------------------------------------------------------------------------------
sweep.res.list <- paramSweep_v3(seu_1, PCs = 1:20, sct = FALSE)
sweep.stats <- summarizeSweep(sweep.res.list, GT = FALSE)
bcmvn <- find.pK(sweep.stats)
bcmvn

## Homotypic Doublet Proportion Estimate -------------------------------------------------------------------------------------
annotations <- seu_1@meta.data$seurat_clusters
homotypic.prop <- modelHomotypic(annotations)           ## ex: annotations <- seu@meta.data$ClusteringResults
nExp_poi <- round(doublet_rates[sample_itor]*nrow(seu_1@meta.data))  ## Assuming 7.5% doublet formation rate - tailor for your dataset
nExp_poi.adj <- round(nExp_poi*(1-homotypic.prop))

## Run DoubletFinder with varying classification stringencies ----------------------------------------------------------------
seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.005, nExp = nExp_poi, reuse.pANN = FALSE, sct = FALSE)
seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.005, nExp = nExp_poi.adj, reuse.pANN = FALSE, sct = FALSE)

seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.07, nExp = nExp_poi, reuse.pANN = FALSE, sct = FALSE)
seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.07, nExp = nExp_poi.adj, reuse.pANN = FALSE, sct = FALSE)

seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.17, nExp = nExp_poi, reuse.pANN = FALSE, sct = FALSE)
seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.17, nExp = nExp_poi.adj, reuse.pANN = FALSE, sct = FALSE)

## Assign classification
seu_1$DoubletFinder <- "Singlet"
seu_1$DoubletFinder[seu_1$DF.classifications_0.25_0.005_44 == "Doublet"] <- "Doublet (high likelyhood)"
seu_1$DoubletFinder[seu_1$DF.classifications_0.25_0.005_44 != "Doublet" &
                    seu_1$DF.classifications_0.25_0.005_48 == "Doublet"] <- "Doublet (low likelyhood)"

## Assign classification
seu_1$DoubletFinder_pK <- "Singlet"
seu_1$DoubletFinder_pK[seu_1$DF.classifications_0.25_0.07_44 == "Doublet"] <- "Doublet (high likelyhood)"
seu_1$DoubletFinder_pK[seu_1$DF.classifications_0.25_0.07_44 != "Doublet" &
                          seu_1$DF.classifications_0.25_0.07_48 == "Doublet"] <- "Doublet (low likelyhood)"

## Assign classification
seu_1$DoubletFinder_pK2 <- "Singlet"
seu_1$DoubletFinder_pK2[seu_1$DF.classifications_0.25_0.17_44 == "Doublet"] <- "Doublet (high likelyhood)"
seu_1$DoubletFinder_pK2[seu_1$DF.classifications_0.25_0.17_44 != "Doublet" &
                          seu_1$DF.classifications_0.25_0.17_48 == "Doublet"] <- "Doublet (low likelyhood)"
```

We are viewing two pK values due to this potential issue https://github.com/chris-mcginnis-ucsf/DoubletFinder/issues/130

```{r, fig.width=18, fig.height=4}
p1 <- DimPlot(seu_1, group.by = "DoubletFinder")
p2 <- DimPlot(seu_1, group.by = "DoubletFinder_pK")
p3 <- DimPlot(seu_1, group.by = "DoubletFinder_pK2")
p1 + p2 + p3
```

```{r, fig.width=18, fig.height=4}
p1 <- VlnPlot(seu_1, features = c("nFeature_RNA"), group.by = "DoubletFinder" , pt.size =  0.01)
p2 <- VlnPlot(seu_1, features = c("nFeature_RNA"), group.by = "DoubletFinder_pK", pt.size =  0.01)
p3 <- VlnPlot(seu_1, features = c("nFeature_RNA"), group.by = "DoubletFinder_pK2", pt.size =  0.01)
cowplot::plot_grid(p1, p2, p3, ncol = 3)
```

```{r}
seu$DoubletFinder[match(colnames(seu_1), colnames(seu))] <- seu_1$DoubletFinder
```


## p3

```{r}
sample_itor <- "p3"
seu_1 <- seu[,seu$sample == sample_itor]

## Pre-process Seurat object (standard) --------------------------------------------------------------------------------------
seu_1 <- NormalizeData(seu_1)
seu_1 <- FindVariableFeatures(seu_1, selection.method = "vst", nfeatures = 2000)
seu_1 <- ScaleData(seu_1)
seu_1 <- RunPCA(seu_1)
seu_1 <- RunTSNE(seu_1, dims = 1:20)
seu_1 <- FindNeighbors(object = seu_1, reduction = "pca", dims = 1:20, verbose = TRUE)
seu_1 <- FindClusters(seu_1, dims = 1:20, resolution = 0.6)
## pK Identification (no ground-truth) ---------------------------------------------------------------------------------------
sweep.res.list <- paramSweep_v3(seu_1, PCs = 1:20, sct = FALSE)
sweep.stats <- summarizeSweep(sweep.res.list, GT = FALSE)
bcmvn <- find.pK(sweep.stats)
bcmvn

## Homotypic Doublet Proportion Estimate -------------------------------------------------------------------------------------
annotations <- seu_1@meta.data$seurat_clusters
homotypic.prop <- modelHomotypic(annotations)           ## ex: annotations <- seu@meta.data$ClusteringResults
nExp_poi <- round(doublet_rates[sample_itor]*nrow(seu_1@meta.data))  ## Assuming 7.5% doublet formation rate - tailor for your dataset
nExp_poi.adj <- round(nExp_poi*(1-homotypic.prop))

## Run DoubletFinder with varying classification stringencies ----------------------------------------------------------------
seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.005, nExp = nExp_poi, reuse.pANN = FALSE, sct = FALSE)
seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.005, nExp = nExp_poi.adj, reuse.pANN = FALSE, sct = FALSE)

seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.28, nExp = nExp_poi, reuse.pANN = FALSE, sct = FALSE)
seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.28, nExp = nExp_poi.adj, reuse.pANN = FALSE, sct = FALSE)

## Assign classification
seu_1$DoubletFinder <- "Singlet"
seu_1$DoubletFinder[seu_1$DF.classifications_0.25_0.005_308 == "Doublet"] <- "Doublet (high likelyhood)"
seu_1$DoubletFinder[seu_1$DF.classifications_0.25_0.005_308 != "Doublet" &
                    seu_1$DF.classifications_0.25_0.005_333 == "Doublet"] <- "Doublet (low likelyhood)"

## Assign classification
seu_1$DoubletFinder_pK <- "Singlet"
seu_1$DoubletFinder_pK[seu_1$DF.classifications_0.25_0.28_308 == "Doublet"] <- "Doublet (high likelyhood)"
seu_1$DoubletFinder_pK[seu_1$DF.classifications_0.25_0.28_308 != "Doublet" &
                          seu_1$DF.classifications_0.25_0.28_333 == "Doublet"] <- "Doublet (low likelyhood)"
```

We are viewing two pK values due to this potential issue https://github.com/chris-mcginnis-ucsf/DoubletFinder/issues/130

```{r, fig.width=12, fig.height=4}
p1 <- DimPlot(seu_1, group.by = "DoubletFinder")
p2 <- DimPlot(seu_1, group.by = "DoubletFinder_pK")
p1 + p2
```

```{r, fig.width=12, fig.height=4}
p1 <- VlnPlot(seu_1, features = c("nFeature_RNA"), group.by = "DoubletFinder" , pt.size =  0.01)
p2 <- VlnPlot(seu_1, features = c("nFeature_RNA"), group.by = "DoubletFinder_pK", pt.size =  0.01)
cowplot::plot_grid(p1, p2, ncol = 2)
```

```{r}
seu$DoubletFinder[match(colnames(seu_1), colnames(seu))] <- seu_1$DoubletFinder
```

## p5

```{r}
sample_itor <- "p5"
seu_1 <- seu[,seu$sample == sample_itor]

## Pre-process Seurat object (standard) --------------------------------------------------------------------------------------
seu_1 <- NormalizeData(seu_1)
seu_1 <- FindVariableFeatures(seu_1, selection.method = "vst", nfeatures = 2000)
seu_1 <- ScaleData(seu_1)
seu_1 <- RunPCA(seu_1)
seu_1 <- RunTSNE(seu_1, dims = 1:20)
seu_1 <- FindNeighbors(object = seu_1, reduction = "pca", dims = 1:20, verbose = TRUE)
seu_1 <- FindClusters(seu_1, dims = 1:20, resolution = 0.6)
## pK Identification (no ground-truth) ---------------------------------------------------------------------------------------
sweep.res.list <- paramSweep_v3(seu_1, PCs = 1:20, sct = FALSE)
sweep.stats <- summarizeSweep(sweep.res.list, GT = FALSE)
bcmvn <- find.pK(sweep.stats)
bcmvn

## Homotypic Doublet Proportion Estimate -------------------------------------------------------------------------------------
annotations <- seu_1@meta.data$seurat_clusters
homotypic.prop <- modelHomotypic(annotations)           ## ex: annotations <- seu@meta.data$ClusteringResults
nExp_poi <- round(doublet_rates[sample_itor]*nrow(seu_1@meta.data))  ## Assuming 7.5% doublet formation rate - tailor for your dataset
nExp_poi.adj <- round(nExp_poi*(1-homotypic.prop))

## Run DoubletFinder with varying classification stringencies ----------------------------------------------------------------
seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.005, nExp = nExp_poi, reuse.pANN = FALSE, sct = FALSE)
seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.005, nExp = nExp_poi.adj, reuse.pANN = FALSE, sct = FALSE)

## Assign classification
seu_1$DoubletFinder <- "Singlet"
seu_1$DoubletFinder[seu_1$DF.classifications_0.25_0.005_12 == "Doublet"] <- "Doublet (high likelyhood)"
seu_1$DoubletFinder[seu_1$DF.classifications_0.25_0.005_12 != "Doublet" &
                    seu_1$DF.classifications_0.25_0.005_14 == "Doublet"] <- "Doublet (low likelyhood)"

```

We are viewing two pK values due to this potential issue https://github.com/chris-mcginnis-ucsf/DoubletFinder/issues/130

```{r, fig.width=6, fig.height=4}
p1 <- DimPlot(seu_1, group.by = "DoubletFinder")
p1 
```

```{r, fig.width=6, fig.height=4}
p1 <- VlnPlot(seu_1, features = c("nFeature_RNA"), group.by = "DoubletFinder" , pt.size =  0.01)
p1
```

```{r}
seu$DoubletFinder[match(colnames(seu_1), colnames(seu))] <- seu_1$DoubletFinder
```

## p6

```{r}
sample_itor <- "p6"
seu_1 <- seu[,seu$sample == sample_itor]

## Pre-process Seurat object (standard) --------------------------------------------------------------------------------------
seu_1 <- NormalizeData(seu_1)
seu_1 <- FindVariableFeatures(seu_1, selection.method = "vst", nfeatures = 2000)
seu_1 <- ScaleData(seu_1)
seu_1 <- RunPCA(seu_1)
seu_1 <- RunTSNE(seu_1, dims = 1:20)
seu_1 <- FindNeighbors(object = seu_1, reduction = "pca", dims = 1:20, verbose = TRUE)
seu_1 <- FindClusters(seu_1, dims = 1:20, resolution = 0.6)
## pK Identification (no ground-truth) ---------------------------------------------------------------------------------------
sweep.res.list <- paramSweep_v3(seu_1, PCs = 1:20, sct = FALSE)
sweep.stats <- summarizeSweep(sweep.res.list, GT = FALSE)
bcmvn <- find.pK(sweep.stats)
bcmvn

## Homotypic Doublet Proportion Estimate -------------------------------------------------------------------------------------
annotations <- seu_1@meta.data$seurat_clusters
homotypic.prop <- modelHomotypic(annotations)           ## ex: annotations <- seu@meta.data$ClusteringResults
nExp_poi <- round(doublet_rates[sample_itor]*nrow(seu_1@meta.data))  ## Assuming 7.5% doublet formation rate - tailor for your dataset
nExp_poi.adj <- round(nExp_poi*(1-homotypic.prop))

## Run DoubletFinder with varying classification stringencies ----------------------------------------------------------------
seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.005, nExp = nExp_poi, reuse.pANN = FALSE, sct = FALSE)
seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.005, nExp = nExp_poi.adj, reuse.pANN = FALSE, sct = FALSE)

seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.02, nExp = nExp_poi, reuse.pANN = FALSE, sct = FALSE)
seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.02, nExp = nExp_poi.adj, reuse.pANN = FALSE, sct = FALSE)

## Assign classification
seu_1$DoubletFinder <- "Singlet"
seu_1$DoubletFinder[seu_1$DF.classifications_0.25_0.005_44 == "Doublet"] <- "Doublet (high likelyhood)"
seu_1$DoubletFinder[seu_1$DF.classifications_0.25_0.005_44 != "Doublet" &
                    seu_1$DF.classifications_0.25_0.005_48 == "Doublet"] <- "Doublet (low likelyhood)"

## Assign classification
seu_1$DoubletFinder_pK <- "Singlet"
seu_1$DoubletFinder_pK[seu_1$DF.classifications_0.25_0.02_44 == "Doublet"] <- "Doublet (high likelyhood)"
seu_1$DoubletFinder_pK[seu_1$DF.classifications_0.25_0.02_44 != "Doublet" &
                          seu_1$DF.classifications_0.25_0.02_48 == "Doublet"] <- "Doublet (low likelyhood)"
```

We are viewing two pK values due to this potential issue https://github.com/chris-mcginnis-ucsf/DoubletFinder/issues/130

```{r, fig.width=12, fig.height=4}
p1 <- DimPlot(seu_1, group.by = "DoubletFinder")
p2 <- DimPlot(seu_1, group.by = "DoubletFinder_pK")
p1 + p2
```

```{r, fig.width=12, fig.height=4}
p1 <- VlnPlot(seu_1, features = c("nFeature_RNA"), group.by = "DoubletFinder" , pt.size =  0.01)
p2 <- VlnPlot(seu_1, features = c("nFeature_RNA"), group.by = "DoubletFinder_pK", pt.size =  0.01)
cowplot::plot_grid(p1, p2, ncol = 2)
```

```{r}
seu$DoubletFinder[match(colnames(seu_1), colnames(seu))] <- seu_1$DoubletFinder
```

## p8

```{r}
sample_itor <- "p8"
seu_1 <- seu[,seu$sample == sample_itor]

## Pre-process Seurat object (standard) --------------------------------------------------------------------------------------
seu_1 <- NormalizeData(seu_1)
seu_1 <- FindVariableFeatures(seu_1, selection.method = "vst", nfeatures = 2000)
seu_1 <- ScaleData(seu_1)
seu_1 <- RunPCA(seu_1)
seu_1 <- RunTSNE(seu_1, dims = 1:20)
seu_1 <- FindNeighbors(object = seu_1, reduction = "pca", dims = 1:20, verbose = TRUE)
seu_1 <- FindClusters(seu_1, dims = 1:20, resolution = 0.6)
## pK Identification (no ground-truth) ---------------------------------------------------------------------------------------
sweep.res.list <- paramSweep_v3(seu_1, PCs = 1:20, sct = FALSE)
sweep.stats <- summarizeSweep(sweep.res.list, GT = FALSE)
bcmvn <- find.pK(sweep.stats)
bcmvn

## Homotypic Doublet Proportion Estimate -------------------------------------------------------------------------------------
annotations <- seu_1@meta.data$seurat_clusters
homotypic.prop <- modelHomotypic(annotations)           ## ex: annotations <- seu@meta.data$ClusteringResults
nExp_poi <- round(doublet_rates[sample_itor]*nrow(seu_1@meta.data))  ## Assuming 7.5% doublet formation rate - tailor for your dataset
nExp_poi.adj <- round(nExp_poi*(1-homotypic.prop))

## Run DoubletFinder with varying classification stringencies ----------------------------------------------------------------
seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.005, nExp = nExp_poi, reuse.pANN = FALSE, sct = FALSE)
seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.005, nExp = nExp_poi.adj, reuse.pANN = FALSE, sct = FALSE)

## Assign classification
seu_1$DoubletFinder <- "Singlet"
seu_1$DoubletFinder[seu_1$DF.classifications_0.25_0.005_47 == "Doublet"] <- "Doublet (high likelyhood)"
seu_1$DoubletFinder[seu_1$DF.classifications_0.25_0.005_47 != "Doublet" &
                    seu_1$DF.classifications_0.25_0.005_51 == "Doublet"] <- "Doublet (low likelyhood)"

```

```{r, fig.width=6, fig.height=4}
p1 <- DimPlot(seu_1, group.by = "DoubletFinder")
p1
```

```{r, fig.width=6, fig.height=4}
p1 <- VlnPlot(seu_1, features = c("nFeature_RNA"), group.by = "DoubletFinder" , pt.size =  0.01)
p1
```

```{r}
seu$DoubletFinder[match(colnames(seu_1), colnames(seu))] <- seu_1$DoubletFinder
```

## p9

```{r}
sample_itor <- "p9"
seu_1 <- seu[,seu$sample == sample_itor]

## Pre-process Seurat object (standard) --------------------------------------------------------------------------------------
seu_1 <- NormalizeData(seu_1)
seu_1 <- FindVariableFeatures(seu_1, selection.method = "vst", nfeatures = 2000)
seu_1 <- ScaleData(seu_1)
seu_1 <- RunPCA(seu_1)
seu_1 <- RunTSNE(seu_1, dims = 1:20)
seu_1 <- FindNeighbors(object = seu_1, reduction = "pca", dims = 1:20, verbose = TRUE)
seu_1 <- FindClusters(seu_1, dims = 1:20, resolution = 0.6)
## pK Identification (no ground-truth) ---------------------------------------------------------------------------------------
sweep.res.list <- paramSweep_v3(seu_1, PCs = 1:20, sct = FALSE)
sweep.stats <- summarizeSweep(sweep.res.list, GT = FALSE)
bcmvn <- find.pK(sweep.stats)
bcmvn

## Homotypic Doublet Proportion Estimate -------------------------------------------------------------------------------------
annotations <- seu_1@meta.data$seurat_clusters
homotypic.prop <- modelHomotypic(annotations)           ## ex: annotations <- seu@meta.data$ClusteringResults
nExp_poi <- round(doublet_rates[sample_itor]*nrow(seu_1@meta.data))  ## Assuming 7.5% doublet formation rate - tailor for your dataset
nExp_poi.adj <- round(nExp_poi*(1-homotypic.prop))

## Run DoubletFinder with varying classification stringencies ----------------------------------------------------------------
seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.005, nExp = nExp_poi, reuse.pANN = FALSE, sct = FALSE)
seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.005, nExp = nExp_poi.adj, reuse.pANN = FALSE, sct = FALSE)

## Assign classification
seu_1$DoubletFinder <- "Singlet"
seu_1$DoubletFinder[seu_1$DF.classifications_0.25_0.005_240 == "Doublet"] <- "Doublet (high likelyhood)"
seu_1$DoubletFinder[seu_1$DF.classifications_0.25_0.005_240 != "Doublet" &
                    seu_1$DF.classifications_0.25_0.005_256 == "Doublet"] <- "Doublet (low likelyhood)"
```


```{r, fig.width=6, fig.height=4}
p1 <- DimPlot(seu_1, group.by = "DoubletFinder")
p1 
```

```{r, fig.width=6, fig.height=4}
p1 <- VlnPlot(seu_1, features = c("nFeature_RNA"), group.by = "DoubletFinder" , pt.size =  0.01)
p1
```

```{r}
seu$DoubletFinder[match(colnames(seu_1), colnames(seu))] <- seu_1$DoubletFinder
```

## p10

```{r}
sample_itor <- "p10"
seu_1 <- seu[,seu$sample == sample_itor]

## Pre-process Seurat object (standard) --------------------------------------------------------------------------------------
seu_1 <- NormalizeData(seu_1)
seu_1 <- FindVariableFeatures(seu_1, selection.method = "vst", nfeatures = 2000)
seu_1 <- ScaleData(seu_1)
seu_1 <- RunPCA(seu_1)
seu_1 <- RunTSNE(seu_1, dims = 1:20)
seu_1 <- FindNeighbors(object = seu_1, reduction = "pca", dims = 1:20, verbose = TRUE)
seu_1 <- FindClusters(seu_1, dims = 1:20, resolution = 0.6)
## pK Identification (no ground-truth) ---------------------------------------------------------------------------------------
sweep.res.list <- paramSweep_v3(seu_1, PCs = 1:20, sct = FALSE)
sweep.stats <- summarizeSweep(sweep.res.list, GT = FALSE)
bcmvn <- find.pK(sweep.stats)
bcmvn

## Homotypic Doublet Proportion Estimate -------------------------------------------------------------------------------------
annotations <- seu_1@meta.data$seurat_clusters
homotypic.prop <- modelHomotypic(annotations)           ## ex: annotations <- seu@meta.data$ClusteringResults
nExp_poi <- round(doublet_rates[sample_itor]*nrow(seu_1@meta.data))  ## Assuming 7.5% doublet formation rate - tailor for your dataset
nExp_poi.adj <- round(nExp_poi*(1-homotypic.prop))

## Run DoubletFinder with varying classification stringencies ----------------------------------------------------------------
seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.005, nExp = nExp_poi, reuse.pANN = FALSE, sct = FALSE)
seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.005, nExp = nExp_poi.adj, reuse.pANN = FALSE, sct = FALSE)

seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.02, nExp = nExp_poi, reuse.pANN = FALSE, sct = FALSE)
seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.02, nExp = nExp_poi.adj, reuse.pANN = FALSE, sct = FALSE)

## Assign classification
seu_1$DoubletFinder <- "Singlet"
seu_1$DoubletFinder[seu_1$DF.classifications_0.25_0.005_72 == "Doublet"] <- "Doublet (high likelyhood)"
seu_1$DoubletFinder[seu_1$DF.classifications_0.25_0.005_72 != "Doublet" &
                    seu_1$DF.classifications_0.25_0.005_77 == "Doublet"] <- "Doublet (low likelyhood)"

## Assign classification
seu_1$DoubletFinder_pK <- "Singlet"
seu_1$DoubletFinder_pK[seu_1$DF.classifications_0.25_0.02_72 == "Doublet"] <- "Doublet (high likelyhood)"
seu_1$DoubletFinder_pK[seu_1$DF.classifications_0.25_0.02_72 != "Doublet" &
                          seu_1$DF.classifications_0.25_0.02_77 == "Doublet"] <- "Doublet (low likelyhood)"
```


```{r, fig.width=12, fig.height=4}
p1 <- DimPlot(seu_1, group.by = "DoubletFinder")
p2 <- DimPlot(seu_1, group.by = "DoubletFinder_pK")
p1 + p2
```

```{r, fig.width=12, fig.height=4}
p1 <- VlnPlot(seu_1, features = c("nFeature_RNA"), group.by = "DoubletFinder" , pt.size =  0.01)
p2 <- VlnPlot(seu_1, features = c("nFeature_RNA"), group.by = "DoubletFinder_pK", pt.size =  0.01)
cowplot::plot_grid(p1, p2, ncol = 2)
```

```{r}
seu$DoubletFinder[match(colnames(seu_1), colnames(seu))] <- seu_1$DoubletFinder
```

## p11

```{r}
sample_itor <- "p11"
seu_1 <- seu[,seu$sample == sample_itor]

## Pre-process Seurat object (standard) --------------------------------------------------------------------------------------
seu_1 <- NormalizeData(seu_1)
seu_1 <- FindVariableFeatures(seu_1, selection.method = "vst", nfeatures = 2000)
seu_1 <- ScaleData(seu_1)
seu_1 <- RunPCA(seu_1)
seu_1 <- RunTSNE(seu_1, dims = 1:20)
seu_1 <- FindNeighbors(object = seu_1, reduction = "pca", dims = 1:20, verbose = TRUE)
seu_1 <- FindClusters(seu_1, dims = 1:20, resolution = 0.6)
## pK Identification (no ground-truth) ---------------------------------------------------------------------------------------
sweep.res.list <- paramSweep_v3(seu_1, PCs = 1:20, sct = FALSE)
sweep.stats <- summarizeSweep(sweep.res.list, GT = FALSE)
bcmvn <- find.pK(sweep.stats)
bcmvn

## Homotypic Doublet Proportion Estimate -------------------------------------------------------------------------------------
annotations <- seu_1@meta.data$seurat_clusters
homotypic.prop <- modelHomotypic(annotations)           ## ex: annotations <- seu@meta.data$ClusteringResults
nExp_poi <- round(doublet_rates[sample_itor]*nrow(seu_1@meta.data))  ## Assuming 7.5% doublet formation rate - tailor for your dataset
nExp_poi.adj <- round(nExp_poi*(1-homotypic.prop))

## Run DoubletFinder with varying classification stringencies ----------------------------------------------------------------
seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.005, nExp = nExp_poi, reuse.pANN = FALSE, sct = FALSE)
seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.005, nExp = nExp_poi.adj, reuse.pANN = FALSE, sct = FALSE)

seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.15, nExp = nExp_poi, reuse.pANN = FALSE, sct = FALSE)
seu_1 <- doubletFinder_v3(seu_1, PCs = 1:20, pN = 0.25, pK = 0.15, nExp = nExp_poi.adj, reuse.pANN = FALSE, sct = FALSE)

## Assign classification
seu_1$DoubletFinder <- "Singlet"
seu_1$DoubletFinder[seu_1$DF.classifications_0.25_0.005_73 == "Doublet"] <- "Doublet (high likelyhood)"
seu_1$DoubletFinder[seu_1$DF.classifications_0.25_0.005_73 != "Doublet" &
                    seu_1$DF.classifications_0.25_0.005_80 == "Doublet"] <- "Doublet (low likelyhood)"

## Assign classification
seu_1$DoubletFinder_pK <- "Singlet"
seu_1$DoubletFinder_pK[seu_1$DF.classifications_0.25_0.15_73 == "Doublet"] <- "Doublet (high likelyhood)"
seu_1$DoubletFinder_pK[seu_1$DF.classifications_0.25_0.15_73 != "Doublet" &
                          seu_1$DF.classifications_0.25_0.15_80 == "Doublet"] <- "Doublet (low likelyhood)"
```

```{r, fig.width=12, fig.height=4}
p1 <- DimPlot(seu_1, group.by = "DoubletFinder")
p2 <- DimPlot(seu_1, group.by = "DoubletFinder_pK")
p1 + p2
```

```{r, fig.width=12, fig.height=4}
p1 <- VlnPlot(seu_1, features = c("nFeature_RNA"), group.by = "DoubletFinder" , pt.size =  0.01)
p2 <- VlnPlot(seu_1, features = c("nFeature_RNA"), group.by = "DoubletFinder_pK", pt.size =  0.01)
cowplot::plot_grid(p1, p2, ncol = 2)
```

```{r}
seu$DoubletFinder[match(colnames(seu_1), colnames(seu))] <- seu_1$DoubletFinder
```

# visualise the overall results

```{r}
table(seu$DoubletFinder, seu$sample)
```

```{r}
saveRDS(seu@meta.data, "perturb_seq/analysis/preprocessing/rds/seu_allcells_doubletFinder.rds")
```

```{r}
DimPlot(seu, reduction = "tsne", group.by = "DoubletFinder")
```

```{r, fig.height=12, fig.width=15}
DimPlot(seu, reduction = "tsne", group.by = "DoubletFinder", split.by = "sgRNA_group", ncol = 5)
```

# Technical

```{r}
sessionInfo()
```
